\textbf{Automated Reasoning\\Practical Assignment -- Part 1}

### 2022-10-10 docs/paper.tex
[Dinner] Brute-force search

\subsection{Results} % (fold)
\label{sub:dinner_results}
We have run Z3 for every subset of additional constraints with the standard constraints.
We have noticed that Z3 takes too long to decide the cases where constraints A and B are both required.\\
The only combination that was proven to be unsatisfiable was $A,C,D$. This implies that the combination of $A,B,C,D$ is also unsatisfiable.\\
All remaining subsets are satisfiable.\\

\begin{tabular}{ll|llll}
\multicolumn{2}{l|}{} & & & A & A \\
\multicolumn{2}{l|}{\multirow{-2}{*}{Constraints}} & & B & & B \\ \hline
 & & \cellcolor{green!50}SAT & \cellcolor{green!50}SAT & \cellcolor{green!50}SAT & \cellcolor{yellow!50}UNKNOWN \\
 & D & \cellcolor{green!50}SAT & \cellcolor{green!50}SAT & \cellcolor{green!50}\textbf{SAT} & \cellcolor{yellow!50}UNKNOWN \\
C & & \cellcolor{green!50}SAT & \cellcolor{green!50}SAT & \cellcolor{green!50}\textbf{SAT} & \cellcolor{yellow!50}UNKNOWN \\
C & D & \cellcolor{green!50}SAT & \cellcolor{green!50}\textbf{SAT} & \cellcolor{red!50}UNSAT & \cellcolor{red!50}UNSAT 
\end{tabular}

>>>>

\subsection{Results} % (fold)
\label{sub:dinner_results}
We have run Z3 for every subset of additional constraints with the standard constraints.
We have noticed that Z3 takes too long to decide the cases where constraints A and B are both required.\\
The only combination that was proven to be unsatisfiable was $A,C,D$. This implies that the combination of $A,B,C,D$ is also unsatisfiable.\\
We have run a brute-force search using C++ on the rounds to show that A and B can not be both satisfied
All remaining subsets are satisfiable.\\

\begin{tabular}{ll|llll}
\multicolumn{2}{l|}{} & & & A & A \\
\multicolumn{2}{l|}{\multirow{-2}{*}{Constraints}} & & B & & B \\ \hline
 & & \cellcolor{green!50}SAT & \cellcolor{green!50}SAT & \cellcolor{green!50}SAT & \cellcolor{red!30}UNSAT \\
 & D & \cellcolor{green!50}SAT & \cellcolor{green!50}SAT & \cellcolor{green!50}\textbf{SAT} & \cellcolor{red!30}UNSAT \\
C & & \cellcolor{green!50}SAT & \cellcolor{green!50}SAT & \cellcolor{green!50}\textbf{SAT} & \cellcolor{red!30}UNSAT \\
C & D & \cellcolor{green!50}SAT & \cellcolor{green!50}\textbf{SAT} & \cellcolor{red!50}UNSAT & \cellcolor{red!50}UNSAT 
\end{tabular}
